\huge A Usability Evaluation of Tor Launcher

### 2016-11-11 pets2017-paper/pets2017-paper.tex
Proper prime notation.

Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes. Neither the Tor Browser's 5.0.3. Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.

@@

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
An exhaustive list of Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}. End states such as e\# and e\#' are equivalent, but e\#' uses a bridge while e\# does not. This was generated during the inspection process.\\

>>>>

Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes. Neither the Tor Browser's 5.0.3 Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.

@@

\section{Success and Error States in Tor Launcher 5.0.3} 
\label{states} 
An exhaustive list of Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}. End states such as e\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not. This was generated during the inspection process.\\
